Competing Bandits:\\ The Perils of Exploration under Competition \thanks{This is a merged and final version of two conference papers, \citet{CompetingBandits-itcs18} and \citet{CompetingBandits-ec19}, with a unified and streamlined presentation.}

### 2020-07-13 journal paper/content/sec-theory.tex
A few more sentences in HMR.

Next, let us argue that \alg[2] is monotone. We spell out the proof for the sake of intuition. For each $n\in\N$, let $M_n$ be the number of times \alg[1] is invoked in the first $n$ steps of \alg[2], and let $\BIRgr_1(n)$ be the $\BIR$ of the ``greedy choice" after $n-1$ steps of \alg[1]. Let 
    $\mathtt{reg}_2(n) = n\cdot \max_a \mu_a - \rew_2(n)$ 
be the (frequentist) instantaneous regret of \alg[2]. Then by definition of the greedy modification it holds that 
\begin{align}\label{eq:random-BIR}
\E\sbr{ \mathtt{reg}_2(n) \mid M_n = m}
    &= (1-p) \cdot \BIR_1(m) + p \cdot \BIRgr_1(m) .\\
\BIR_2(n)
    &= \E\sbr{ (1-p) \cdot \BIR_1(M_n) + p \cdot \BIRgr_1(M_n) }.
\end{align}
Now, monotonicity of \alg[2] follows from monotonicity of $\BIR_1(\cdot)$ and $\BIRgr_1(\cdot)$.

>>>>

Next, let us argue that \alg[2] is monotone. We spell out the proof for the sake of intuition. For each $n\in\N$, let $M_n$ be the number of times \alg[1] is invoked in the first $n$ steps of \alg[2], and let $\BIRgr_1(n)$ be the $\BIR$ of the ``greedy choice" after $n-1$ steps of \alg[1]. Let 
    $\mathtt{reg}_2(n) = n\cdot \max_a \mu_a - \rew_2(n)$ 
be the (frequentist) instantaneous regret of \alg[2]. Then by definition of the greedy modification it holds that 
\begin{align}\label{eq:random-BIR}
\E\sbr{ \mathtt{reg}_2(n) \mid M_n = m}
    &= (1-p) \cdot \BIR_1(m) + p \cdot \BIRgr_1(m) .\\
\BIR_2(n)
    &= \E\sbr{ (1-p) \cdot \BIR_1(M_n) + p \cdot \BIRgr_1(M_n) }.
\end{align}
Now, monotonicity of $\BIR_2$ follows from monotonicity of $\BIR_1(\cdot)$ and $\BIRgr_1(\cdot)$. The former is assumed, and the latter is the monotonicity-in-information property of the ``greedy step" (see \ascomment{pointer} for a precise formulation and proof).

Thus, the greedy modification is beneficial in competition \emph{and} keeps us inside the set of monotone MAB algorithms. Consequently, if the principals are restricted to choosing monotone MAB algorithms, then non-greedy algorithms cannot be chosen in equilibrium.
